Yield Mapping

### 2016-02-11 Rmd/to-do.Rmd
Developed several flavors of GAM-derived soy and maize grids, and adjusted them to FAO mean projected yields.

# make an html table
# http://r-norberg.blogspot.com/2013/06/generating-tables-using-pander-knitr.html
tabl <- cbind(
  "Item" = c("Plausible Scenario", 
             "Gridded yields",
             "Gridded yields",
             "Upgrade soils", 
             "Filter terrain", 
             "Biodiversity impacts", 
             "Impacts weighting (per Tim)", 
             "Work in economics", 
             "Explore econ versus enviro goals", 
             "Better cropland map, yield estimates", 
             "Updated carbon layers"), 
  "Notes" = c("Single production to follow (Alastair)", 
              "Exact method for variability and production zones, including inability to reach potential yields", 
              "Run with improved soils maps", 
              "With ILUA database (and Nate's help)", 
              "Removable unfarmable areas, add new supporting logic", 
              "Habitat rarity/threatenedness", 
              "Weight carbon and biodiversity equally", 
              "Estimate profitability per pixel. Either input modification or code modification", 
              "See where map overlaps are greatest, most divergent", 
              "Upgrade all maps to SERVIR landcover, and rebase yield estimates on that", "Baccini vegetation carbon + ISRIC grids"),
  "Doing" = c("D", "F*", "U", "U", "D", "D", "D", "L", "D", "F**", "F")
)
print(xtable::xtable(tabl), align = rep("c", dim(table)[2] + 1), type = "html", 
      include.rownames = FALSE)
```
*Temporary soybean grid with bias adjustment from FAO GAEZ yields. Developed weighted merged method for different types of management.

@@

>>>>

# make an html table
# http://r-norberg.blogspot.com/2013/06/generating-tables-using-pander-knitr.html
tabl <- cbind(
  "Item" = c("Plausible Scenario", 
             "Gridded yields",
             "Gridded yields",
             "Upgrade soils", 
             "Filter terrain", 
             "Biodiversity impacts", 
             "Impacts weighting (per Tim)", 
             "Work in economics", 
             "Explore econ versus enviro goals", 
             "Better cropland map, yield estimates", 
             "Updated carbon layers"), 
  "Notes" = c("Single production to follow (Alastair)", 
              "Exact method for variability and production zones, including inability to reach potential yields", 
              "Run with improved soils maps, using two stage regression", 
              "With ILUA database (and Nate's help)", 
              "Removable unfarmable areas, add new supporting logic", 
              "Habitat rarity/threatenedness", 
              "Weight carbon and biodiversity equally", 
              "Estimate profitability per pixel. Either input modification or code modification", 
              "See where map overlaps are greatest, most divergent", 
              "Upgrade all maps to SERVIR landcover, and rebase yield estimates on that", "Baccini vegetation carbon + ISRIC grids"),
  "Doing" = c("D", "F*", "F", "U", "F", "F", "F***", "L", "D", "F**", "F")
)
print(xtable::xtable(tabl), align = rep("c", dim(table)[2] + 1), type = "html", 
      include.rownames = FALSE)
```
*Temporary soybean grid with bias adjustment from FAO GAEZ yields. Developed weighted merged method for different types of management.

@@

***This is what the model effectively does, and issue has been resolved.

### 2016-02-11 Rmd/yield-predictors.rmd
Developed several flavors of GAM-derived soy and maize grids, and adjusted them to FAO mean projected yields.

# Create tmean variable
tmu <- foreach(i = 1:length(sindu2)) %dopar% { #  i <- 1
  ind <- which(sind == sindu2[i])
  tmu <- (tmax[[ind]] + tmin[[ind]]) / 2 - 273.15
}
writeRaster(stack(tmu), filename = fp(p_clim, "tmu.tif"), overwrite = TRUE)

@@

# growing degree day and killing degree days
kdd <- stack(kdy <- foreach(i = 1:length(tmu)) %dopar% calc(tmu[[i]], kdd))
writeRaster(kdd, filename = fp(p_clim, "kdd.tif"), overwrite = TRUE)
gdd30 <- stack(gdy <- foreach(i = 1:length(tmu)) %dopar% calc(tmu[[i]], gdd830))
writeRaster(gdd30, filename = fp(p_clim, "gdd30.tif"), overwrite = TRUE)
gdd <- stack(gdy <- foreach(i = 1:length(tmu)) %dopar% calc(tmu[[i]], gddf))
writeRaster(gdd30, filename = fp(p_clim, "gdd.tif"), overwrite = TRUE)

@@

```{r, eval = FALSE}
# Organize rainfall
climnms <- c("rftot", "ndjftot", "^djfmtot", "^jfmtot", "jantot", "febtot",
             "octtot", "kdd", "gdd\\.", "gdd30", "nkilljan", "nkillfeb",
             "tmax_ano", "tmax_gs", "srtot_ano", "srmu_ano", "srtot_gs",
             "srmu_gs1", "srmu_gs2", "srmu_gs3")
bnms <- sapply(climnms, function(x) dir(p_clim, pattern = x, full.names = TRUE))

@@

onms <- c("MAP", "MSP", "DJFMP", "JFMP", "JP", "FP", "OP", "KDD", "GDD", 
          "GDDL", "NKJ", "NKF", "ATMX", "STMX", "ASRT", "ASRM", "SSRT", "SSRMI",
          "SSRMII", "SSRMIII")
climl <- lapply(1:length(blist), function(x) {
  r <- blist[[x]]
  names(r) <- paste0(onms[x], 1:nlayers(r))
  r
})
names(climl) <- onms

>>>>

# Create tmean variable
tmu <- foreach(i = 1:length(sindu2)) %dopar% { #  i <- 1
  ind <- which(sind == sindu2[i])
  tmu <- (tmax[[ind]] + tmin[[ind]]) / 2 - 273.15
  round(tmu, 2)
}
tmu <- stack(tmu)

# tmu for the DJFM
# sindu <- unique(sind)[-1]
djfmind2 <- djfmind[which(sind %in% sindu2)]
for(i in sindu2) djfmind2[which(djfmind2 == i)] <- i - 31 
sindu3 <- unique(djfmind2)[-1]
tmuseas <- stack(foreach(i = 1:length(sindu3)) %dopar% { #  i <- 1
  ind <- which(djfmind2 == sindu3[i])
  calc(tmu[[ind]], mean)
})
writeRaster(tmuseas, filename = fp(p_clim, "tmu.tif"), overwrite = TRUE)

@@

# growing degree day and killing degree days
kdd <- stack(kdy <- foreach(i = 1:length(tmu)) %dopar% calc(tmu[[i]], kdd))
writeRaster(kdd, filename = fp(p_clim, "kdd.tif"), overwrite = TRUE)
gdd30 <- stack(gdy <- foreach(i = 1:length(tmu)) %dopar% calc(tmu[[i]], gdd830))
writeRaster(gdd30, filename = fp(p_clim, "gdd30.tif"), overwrite = TRUE)
gdd <- stack(gdy <- foreach(i = 1:length(tmu)) %dopar% calc(tmu[[i]], gddf))
# writeRaster(gdd, filename = fp(p_clim, "gdd.tif"), overwrite = TRUE)

@@

```{r, eval = FALSE}
# Organize rainfall
climnms <- c("rftot", "ndjftot", "^djfmtot", "^jfmtot", "jantot", "febtot",
             "octtot", "tmu", "kdd", "gdd\\.", "gdd30", "nkilljan", "nkillfeb",
             "tmax_ano", "tmax_gs", "srtot_ano", "srmu_ano", "srtot_gs",
             "srmu_gs1", "srmu_gs2", "srmu_gs3")
bnms <- sapply(climnms, function(x) dir(p_clim, pattern = x, full.names = TRUE))

@@

onms <- c("MAP", "MSP", "DJFMP", "JFMP", "JP", "FP", "OP", "TMU", "KDD", "GDD", 
          "GDDL", "NKJ", "NKF", "ATMX", "STMX", "ASRT", "ASRM", "SSRT", "SSRMI",
          "SSRMII", "SSRMIII")
climl <- lapply(1:length(blist), function(x) {
  r <- blist[[x]]
  names(r) <- paste0(onms[x], 1:nlayers(r))
  r
})
names(climl) <- onms
